### 2013-11-18 Paper_Markdown.Rmd
Changed the bias plot to fix y axis and sqrt the yaxis values.

ggplot(model.samp, aes(x = dissim, y = bias, group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, scales='free_y', nrow = 1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Bootstrap Variance')

>>>>

ggplot(model.samp, aes(x = dissim, y = sqrt(bias), group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, scales='free_y', nrow = 1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Bias (RMSEP)')
